---
title: "Мой отчет"
author: "Я"
date: '29 марта 2017 г '
output: html_document
---

```{r}
iris
iris$Sepal.Length
mean(iris$Sepal.Length)
x=mean(iris$Sepal.Length)
x
iris$Sepal.Width
mean(iris$Sepal.Width)
y=mean(iris$Sepal.Width)
y
iris$Petal.Length
mean(iris$Petal.Length)
z=mean(iris$Petal.Length)
z
iris$Petal.Width
mean(iris$Petal.Width)
h=mean(iris$Petal.Width)
h
list(x,y,x,h)
length(list(x,y,x,h))
```


```{r}
iris
y = c()
for (i in 1:150)
{x = sum(iris[i,1:4]/4) 
  y = c(x,y)}
y
```


```{r}
DNA = c("A","G","T","C")
DNA=summary(DNA, size = 1000, replece=T)
DNA=factor(DNA)
summary(DNA)/length(DNA)
dna_at=c(DNA[1],DNA[4]); dna_at
dna_at
```


```{r}
letters
abc=sample(letters, size=10000, replace=T)
abc
for(i in length(abc))
if(abc[i]=="a"|abc[i]=="e"|abc[i]=="i"|abc[i]=="o"|abc[i]=="u"|abc[i]=="y")
{vowel=y+1}
"else{vowel+0}"
'vowel'
```


```{r}
median <- function(x) { 
  z=sort(x) 
  if((length(z)%%2)!=0){ 
    result = z[(length(x)/2)+1] 
  } 
  else 
    result = (z[length(x)/2]+z[length(x)/2+1])/2 
  return(result) 
} 
median(iris$Sepal.Length)
```


```{r}
iris
names(iris)
x=iris$Sepal.Length[1:50]
y=iris$Petal.Length[1:50]
plot(x,y,main="The dependence of the length of the sepal length of petal to form setosa", xlab="Sepal.Length",ylab="$Petal.Length", col="purple")
x=NULL
y=NULL
x=iris$Sepal.Length[51:101]
y=iris$Petal.Length[51:101]
plot(x,y,main="The dependence of the length of the sepal length of petal to form versicolor", xlab="Sepal.Length",ylab="$Petal.Length", col="red")
x=NULL
y=NULL
x=iris$Sepal.Length[101:150]
y=iris$Petal.Length[101:150]
plot(x,y,main="The dependence of the length of the sepal length of petal to form virginica", xlab="Sepal.Length",ylab="$Petal.Length", col="orange")
x=NULL
y=NULL
```


```{r}
library(ggplot2)
diamonds
tapply(diamonds$price[diamonds$price >1000], diamonds$clarity[diamonds$price >1000], mean)
```


```{r}
help_Spirmen=function(table,ind)
{
  table=table[order(table[,ind]),]
  table[,ind+2]=1:nrow(table)
  line=table[,ind]
  for (i in as.numeric(names(table(line)[table(line)>1]))){
    sum=0
    for (j in which(line %in% i))
    {
      sum=sum+table[j,ind+2]
    }
    sum=sum/length(which(line %in% i))
    table[which(line %in% i),ind+2]=sum
  }
  return(table)
}
Spirmen=function(x1,x2)
{
  if(length(x1)!=length(x2))
  {
    return("Problem with the lengths of the vectors")
  }
  table=matrix(ncol=5,nrow=length(x1))
  table[,1]=x1
  table[,2]=x2
  table=help_Spirmen(table,1)
  table=help_Spirmen(table,2)
  table[,5]=(table[,3]-table[,4])**2
  sum=sum(table[,5])
  result=1-6*sum/(length(x1)*(length(x1)**2-1))
  return(result)  
}
med=function(elements)
{
  elements=elements[order(elements)]
  if(length(elements)%%2==0)
  {
    n=length(elements)%/%2
    element=(elements[n]+elements[n+1])/2
  }
  else
  {
    element=elements[length(elements)%/%2+1]
  }
  return(element)
}